Introduction

### 2015-07-21 dissertation/problems.tex
reorganize

Then, as \cite{buil2013sparql} confirmed my suspicions that there were
severe stability problems with SPARQL endpoints,
Problem~\ref{prob:syntacticcache} became my main focus, but clearly,
the understanding of the actual usage of caching was inadequate, so I
decided to solve Problem~\ref{prob:sanity} first. This work is
discussed in Section~\ref{sec:consanity}.

To further address Problem~\ref{prob:syntacticcache}, I decided to
write a query planner that could reuse previous results or prefetch
data the system deemed relevant, but then we realised that the current
programming paradigm was quite unhelpful when customising a query
planner for such a purpose. Rather than writing a prototypical query
engine for illustrative purposes, we wanted to integrate it into a
fully compliant SPARQL query engine, and address
problems~\ref{prob:breakdown},~\ref{prob:complexapi}~and~\ref{prob:dontjustpass}. This
is explained in Section~\ref{sec:conpush}

>>>>

Then, as \cite{buil2013sparql} confirmed my suspicions that there were
severe stability problems with SPARQL endpoints,
Problem~\ref{prob:syntacticcache} became my main focus, and I decided
to write a query planner that could reuse previous results or prefetch
data the system deemed relevant, but then we realised that the current
programming paradigm was quite unhelpful when customising a query
planner for such a purpose. Rather than writing a prototypical query
engine for illustrative purposes, we wanted to integrate it into a
fully compliant SPARQL query engine, and address
problems~\ref{prob:breakdown},~\ref{prob:complexapi}~and~\ref{prob:dontjustpass}. This
is explained in Section~\ref{sec:conpush}

Before addressing Problem~\ref{prob:syntacticcache}, I found that the
understanding of the actual usage of caching was inadequate, so I
decided to solve Problem~\ref{prob:sanity} first. This work is
discussed in Section~\ref{sec:consanity}.
